Analyzing the Privacy Paradox Using a Nationally Representative Three-Wave Panel Study

### 2020-07-28 analyses.Rmd
- updated paper for revision

In what follows, we report the measures we collected, including their items, factorial validity, reliability, and ICC. For the measures' longitudinal invariance, see [additional analyses](analyses_additional.Rmd).

@@

1. In general, how concerned are you about your privacy while using the Internet?
2. Are you concerned about online organizations not being who they claim they are?
3. Are you concerned about online identity theft?
4. Are you concerned about people you do not know obtaining personal information about you from your online activities?
5. Are you concerned that if you use your credit card to buy something on the Internet your credit card number will be obtained/intercepted by someone else?
6. Are you concerned that an email you sent may be read by someone else besides the person you sent it to?
7. Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing on the Internet?
8. Are you concerned that website providers are tracking your online activities?
9. Are you concerned that you don’t know what other organizations or website providers are doing with you data?

@@

1. Financial information (bank data, account balances…)
2. Medical information (health, medical records…)
3. Second name
4. First name
5. Residence
6. Street and house number
7. Email address
8. Phone number
9. Photos (of you)
10. Job (past and present)
11. Education

>>>>

In what follows, we report the measures we used for our analyses, including their items, factorial validity, reliability, and ICC.

We conducted confirmatory factor analyses to determine the underlying factor structure and to remove items that showed poor measurement properties (see [additional analyses](analyses_additional.Rmd)).

For the measures' longitudinal invariance, see [additional analyses](analyses_additional.Rmd).

@@

4. Are you concerned about people you do not know obtaining personal information about you from your online activities?
5. Are you concerned that if you use your credit card to buy something on the Internet your credit card number will be obtained/intercepted by someone else?
6. Are you concerned that an email you sent may be read by someone else besides the person you sent it to?
7. Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing on the Internet?
8. Are you concerned that website providers are tracking your online activities?
9. Are you concerned that you don’t know what other organizations or website providers are doing with you data?

@@

&nbsp; 1. Financial information (bank data, account balances…)  
&nbsp; 2. Medical information (health, medical records…)  
&nbsp; 3. Second name  
&nbsp; 4. First name  
&nbsp; 5. Residence  
&nbsp; 6. Street and house number  
&nbsp; 7. Email address  
&nbsp; 8. Phone number  
&nbsp; 10. Job (past and present)  
&nbsp; 11. Education

### 2020-07-28 analyses_additional.Rmd
- updated paper for revision

```{r}
# set-up
no <- 0
name <- "pri_con"
d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"))
model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
print(factan, sort = TRUE, cut = .3)
```

>>>>

```{r}
# set-up
no <- 0
name <- "pri_con"
d_tmp <- select(d_wide, contains(paste0("t1_", name)), -contains("_m"), -contains("_fs"))
model <- fa.parallel(d_tmp, fa = "fa", fm = "ml")
factan <- fa(d_tmp, fm = "ml", nfactors = model$nfact, rotate = "promax")
print(factan, sort = TRUE, cut = .3)
```
